---
title: "Rubric Report"
author: "Kentaro Murayama"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document: default
  word_document: default
params:
  rubricid: 96094
  parenthtml: "report02links.html"
---
```{r setup, echo=FALSE}
library(tidyverse)
library(gridExtra)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# Run prepdata.R and then report02-parepare.R
# Make it into a stand-alone?
load("../out/report.RData")
```

```{r, results='asis'}
cat(paste0("[Return to links.](", params$parenthtml, ")"))
```


# Report on Rubric `r params$rubricid`

Timely assessment of the students' outcome and the rubric itself is critical both in internal assessments - for improving our teaching standards - and external assessments - for securing the accreditation status - in the coming years.
The data of rubrics and their outcomes are readily available in D2L for this purpose.

Here, the distributions of achievement levels are displayed for each rubric.
For external assessment, the achievement levels are grouped to "Met" and "Not Met", whose threshold is between "Rudimentary" and "Basic".

```{r graph1, fig.width = 8, fig.height = 8}
x <- sdf %>% filter(RubricId == params$rubricid)
cObjs <- levels(factor(x$ObjectiveNameUpper))
p <- list()
if(length(cObjs) == 0){
  caption <- paste("Distribution of Levels Achieved,\n Rubric", params$rubricid)
  p[[1]] <- ggplot(x, aes(LevelAchieved, fill = Meet)) + geom_bar() +
    labs(title = caption, fill = "Achievement") +
    facet_wrap(~ shortCriterionName)
}else{
  for(j in 1:length(cObjs)){
    Objective <- cObjs[j]
    caption <- paste("Distribution of Levels Achieved,\n Rubric", params$rubricid)
    caption <- paste(caption, ", Objective Group", Objective)
    p[[j]] <- ggplot(x %>% filter(ObjectiveNameUpper == Objective),
                aes(LevelAchieved, fill = Meet)) + geom_bar() +
      labs(title = caption, fill = "Achievement") +
      facet_wrap(~ shortCriterionName)
  }
}
# Finish up with aesthetics
for(j in 1:length(p)){
  pj <- p[[j]] + theme(axis.text.x = element_text(angle = 90)) +
    xlab("Level Achieved") +
    scale_fill_brewer(palette = "Set1", drop = FALSE) +
    scale_x_discrete(drop = FALSE) + theme(aspect.ratio = 1)
  print(pj)
}
```

Moreover, it is important to distinguish those who met the criterion *sufficiently* and *marginally*. The proportion of the students who passed with "Basic" achievement level are highlighted in the following graphs.


```{r graph2, fig.width = 6, fig.height = 6}
x <- sdf %>% filter(RubricId == params$rubricid)
cObjs <- levels(factor(x$ObjectiveNameUpper))
p <- list()
if(length(cObjs) == 0){
  caption <- paste("Distribution of Levels Achieved,\n Rubric", params$rubricid)
  p[[1]] <- ggplot(x,
                   aes(x = shortCriterionName, fill = MeetBasic)) + 
    geom_bar(position = "fill") +
    labs(title = caption, fill = "Achievement")
}else{
  for(j in 1:length(cObjs)){
    Objective <- cObjs[j]
    caption <- paste("Distribution of Levels Achieved,\n Rubric", params$rubricid)
    caption <- paste(caption, ", Objective Group", Objective)
    p[[j]] <- ggplot(x %>% filter(ObjectiveNameUpper == Objective),
                     aes(x = shortCriterionName, fill = MeetBasic)) +
      geom_bar(position = "fill") +
      labs(title = caption, fill = "Achievement")
  }
}
# Finish up with aesthetics
for(j in 1:length(p)){
  pj <- p[[j]] + theme(axis.text.x = element_text(angle = 90)) +
    xlab("Criteria") +
    ylab("Shares") +
    scale_fill_brewer(palette = "Set1", drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    coord_flip()
  print(pj)
}
```
