---
title: "Note to Inspect Rubric Data"
output: html_notebook
---

```{r, echo=FALSE, include=FALSE}
#knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
library(readxl)
```

# Introduction
Not much to explain. I have the data now! Finally! Let's look at it.

# Import Data
Import the data. Jon notified me that D2L has changed its specification recently, so that he can no longer retrieve the data in one go. He had to submit multiple queries (I think?) and put them together. He tried to mimic the format I had for the sample a while ago.
```{r}
fn <- "data/Rubrics.xlsx"
df <- read_xlsx(fn)
head(df)
```

Looks good. Are the variable types recognized appropriately?
```{r}
sapply(df, class)
```

Mostly. Let's change IDs into categorical. Level Achieved as well. Then, summarize the dataset.
```{r}
df <- df %>% mutate(across(c(RubricId:UserId, LevelAchieved), factor),
                    IsScoreOverridden = (IsScoreOverridden == "True"))
summary(df)
```

How many rubrics, students, levels?
```{r}
df %>% summarize(across(where(is.factor), nlevels))
```

Like before, I need to clean up levels. Take a look:
```{r}
levels(df$LevelAchieved)
```

It's "contaminated" by survey questions like majors. Actual achievement levels have additional notes like (65/100), but relatively easy to fix: There's no contradicting values (e.g. Proficient 85% vs Proficient 90%). Just get rid of these notes. There are a few that I don't understand "Level 2", "New Level", etc. I need to check the actual rubric for those. For now, just separate them form the main data frame.

Now, I can filter out rubrics by examining the correspondence with those non-achievement levels like last time. Or, this time, I can merge the data with the course-rubric data from survey first then filter. If individual rubrics are mixed with non-achievement levels (likely), I'll want to handle them at analysis stage...

Import the survey data.
```{r}
fn <- "data/Tracking of Assessment of Student Learning Outcomes Data Collection.xlsx"
print("Excel names are:")
excel_sheets(fn)
res <- read_excel(fn, sheet = "Response0602")
```

As common in survey data, column names are a bit messy.
```{r}
names(res)
```

Rename columns. (Ignore non-rubric columns. The data needed to be corrected manually. The output is stored in another file.)
```{r}
res <- res[1:12]
qs <- names(res)
responder.info <- c("ID", "Started", "Completed", "Email", "Name")
course.info <- c("Semester", "Course")
assessment.info <- c("Assessment Name", "Rubric Usage")
rubric.info <- c("URL", "Intrepretation", "Action for Improvement")
names(res)[1:12] <- c(responder.info, course.info, assessment.info, rubric.info)
head(res)
```

Alright. Convert the types.
```{r}
sapply(res, class)
```

`ID` and `Email` - `Semester` are multiple choice questions, while `Course` and `Assessment Name` are open ended. Before converting column types, let's clean up the data.

First, select rows with rubric usage.
```{r}
res <- res[res$`Rubric Usage` == "Yes", ]
dim(res)
```

Then inspect those two columns.

Course and session? From non-rubric data, I know typos and inconsistency are very common. (Side note: I updated questions in a copy of the survey. **Don't forget to update the questions before the next semester.**)
```{r}
levels(as.factor(res$`Course`))
```

- Retrieve program name. Three letter identifier (mostly).
- Retrieve course number. Three digits.
- Retrieve section ids. Three digits/letters following *some* separator (hyphen or space)
- Watch out for random tab instead of space.

Some experiments:
```{r}
x <- levels(as.factor(res$Course))
x <- str_replace(x, "GW[I|!]", "GW1") # Replace some typos
x <- str_remove(x, "[0-9]{4,}") # Remove leading time stamp
cid1 <- str_match(x, "[A-Z]{2,3}")
cid2 <- str_extract_all(x, "(CD|G[WS])?[0-9]{1,3}", simplify = TRUE)
cbind(x, cid1, cid2)
```

Apply to the data.
```{r}
x <- res$Course

x <- str_replace(x, "GW[I|!]", "GW1") # Replace some typos
x <- str_remove(x, "[0-9]{4,}") # Remove leading time stamp
cid1 <- str_match(x, "[A-Z]{2,3}")
cid2 <- str_extract_all(x, "(CD|G[WS])?[0-9]{1,3}", simplify = TRUE)

res.names <- names(res)
res <- cbind(res, cid1, cid2)
names(res) <- c(res.names, paste0("CID", 1:3))

res$CID1 <- str_replace(res$CID1, "BS[U]?", "BUS") # Replace less critical typo
res$CID3 <- str_replace(res$CID3, "^01", "001") # Replace less critical typo
```

Next, assessment name. Convert and check category numbers.
```{r}
x1 <- levels(as.factor(res$`Assessment Name`))
x2 <- str_to_title(res$`Assessment Name`)
x2 <- levels(as.factor(x2))
length(x1); length(x2)
x2
```

Good enough. I can fix the rest manually. Proceed for now.
```{r}
res$`Assessment Name` <- str_to_title(res$`Assessment Name`)
```


Finally, change the column types.
```{r}
sapply(res, class)
res <- res %>% select(-Course) %>% mutate(across(c(ID, Email:Semester, starts_with("CID")), factor))
summary(res)
```

One more thing. I need an identifier for merge. Extract rubric ID.
```{r}
str_extract_all(res$URL, "rubricId=[0-9]{6}", simplify=TRUE)
```

26 and 94?
```{r}
res[c(26, 94), "ID"]
```

- ID 41 > Neeley's entry. Just split it.
- ID 159 > Ed's entry. It was an error entry. Drop it.

```{r}
res[94, ] <- res[26, ]
```

Neeley entered two assessment names as well.
```{r}
anames <- str_split(res[94, "Assessment Name"], ",", simplify = TRUE)
urls <- str_split(res[94, "URL"], "Burts", simplify = TRUE)

res[26, c("Assessment Name", "URL")] <- c(anames[1], urls[1])
res[94, c("Assessment Name", "URL")] <- c(anames[2], urls[2])
res[c(26, 94), ]
```

```{r}
str_extract_all(res$URL, "rubricId=[0-9]{6}", simplify=TRUE)
```

Then, place the Rubric ID.
```{r}
x <- str_extract_all(res$URL, "rubricId=[0-9]{6}", simplify=TRUE)
res$RubricId <- factor(str_extract_all(x, "[0-9]{6}", simplify=TRUE))
```

Finally, compare rubric IDs. Which of IDs in the D2L data are in survey?
```{r}
levels(df$RubricId) %in% levels(res$RubricId)
```

All of them.

What about the other way? (i.e. In survey, but not in the D2L data)
```{r}
levels(res$RubricId) %in% levels(df$RubricId)
```

Hmm. Several of them...
```{r}
(outcome.miss <- levels(res$RubricId)[!levels(res$RubricId) %in% levels(df$RubricId)])
```

```{r}
res[res$RubricId %in% outcome.miss, c("ID", "Name", "CID1", "Assessment Name")]
```

Keep these in mind.

Are the rubric IDs unique?
```{r}
tbl <- table(res$RubricId)
dups <- tbl[tbl > 1]
dups
```
```{r}
res[res$RubricId %in% names(dups), ]
```
It's getting a bit obnoxious. I can fix these later, even manually. As long as each rubric identify course uniquely, I'm good to go for now.

```{r}
res[res$RubricId==names(dups)[1], ]
# Drop 2, 22
res[res$RubricId==names(dups)[2], ]
# Drop 41 (see the note)
res[res$RubricId==names(dups)[3], ]
# Drop 77 Why resubmit?
res[res$RubricId==names(dups)[4], ]
# Drop 71 ?
res[res$RubricId==names(dups)[5], ]
# Drop 1
res[res$RubricId==names(dups)[6], ]
# Drop 83 ?
res[res$RubricId==names(dups)[7], ]
# Drop 88 ?
res[res$RubricId==names(dups)[8], ]
# Different sections but provided same ID. Actual error. Drop 116.
res[res$RubricId==names(dups)[9], ]
# Drop 37
res[res$RubricId==names(dups)[10], ]
# Drop 93 ?
res[res$RubricId==names(dups)[11], ]
# Drop 92 ?
id.drop <- c(2, 22, 41, 77, 71, 1, 83, 88, 116, 37, 93, 92)
res <- res %>% filter(!ID %in% id.drop)

tbl <- table(res$RubricId)
dups <- tbl[tbl > 1]
dups
```

Good.

Finally, merge the data.

```{r}
res$Course <- with(res, paste(CID1, CID2, CID3))
dim(df)
df <- df %>% left_join(res %>% select(RubricId, Course, `Assessment Name`, Semester), by="RubricId")
dim(df)
```

Take a look.
```{r}
summary(df)
```

# Inspect Data

# Next Action

# Note: For archiving notebook
```
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: false
    number_sections: true
    theme: paper
```