---
title: "Note to Inspect Rubric Data 2"
output: html_notebook
---

```{r, echo=FALSE, include=FALSE}
#knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
library(readxl)
```

# Intro
Let's sort out the data import and munging. Most problems came from the survey data. As noted in the last note, I can manually edit the file rather than fixing them here. Keep the code neat and use it later for error check. No need for further improvement.

## Import D2L
First, import D2L data.
```{r import-d2l}
fn <- "data/Rubrics.xlsx"
df <- read_xlsx(fn) %>%
  mutate(across(c(RubricId:Name, LevelAchieved), factor),
         IsScoreOverridden = (IsScoreOverridden == "True"))
```

## Import Survey
Import the survey. Only the first 12 columns are relevant to those with rubrics.
```{r import-survey}
fn <- "data/Tracking of Assessment of Student Learning Outcomes Data Collection.xlsx"
res <- read_excel(fn, sheet = "Response0602")
res <- res[res[, 9] == "Yes", ] # Use rubrics?
res <- res[1:12]

qs <- names(res)
responder.info <- c("ID", "Started", "Completed", "Email", "Name")
course.info <- c("Semester", "Course")
assessment.info <- c("Assessment Name", "Rubric Usage")
rubric.info <- c("URL", "Intrepretation", "Action for Improvement")
names(res) <- c(responder.info, course.info, assessment.info, rubric.info)
```

Now, clean up the file. Course names have some minor errors. It'll be easier if correcting them and split its components for later use.
```{r clean-course}
x <- res$Course

x <- str_replace(x, "GW[I|!]", "GW1") # Replace some typos
x <- str_remove(x, "[0-9]{4,}") # Remove leading time stamp
cid1 <- str_match(x, "[A-Z]{2,3}")
cid2 <- str_extract_all(x, "(CD|G[WS])?[0-9]{1,3}", simplify = TRUE)
res.names <- names(res)
res <- cbind(res, cid1, cid2)
names(res) <- c(res.names, paste0("CID", 1:3))
res$CID1 <- str_replace(res$CID1, "BS[U]?", "BUS") # Replace less critical typo
res$CID3 <- str_replace(res$CID3, "^01", "001") # Replace less critical typo

```

Assessment names shall be used 'as is', but need to check for errors. There are two changes: Drop Ed's entry. Split Neeley's.
```{r clean-assessment}
res$`Assessment Name` <- str_to_title(res$`Assessment Name`) # Good enough
res[94, ] <- res[26, ]

anames <- str_split(res[94, "Assessment Name"], ",", simplify = TRUE)
urls <- str_split(res[94, "URL"], "Burts", simplify = TRUE)
res[26, c("Assessment Name", "URL")] <- c(anames[1], urls[1])
res[94, c("Assessment Name", "URL")] <- c(anames[2], urls[2])
```

Lastly, prepare for merge. Need to have unique IDs.
```{r extract-rubricid}
x <- str_extract_all(res$URL, "rubricId=[0-9]{6}", simplify=TRUE)
res$RubricId <- factor(str_extract_all(x, "[0-9]{6}", simplify=TRUE))
```
```{r, eval=FALSE}
tbl <- table(res$RubricId)
dups <- tbl[tbl > 1]
res[res$RubricId==names(dups)[1], ]
# Drop 2, 22
res[res$RubricId==names(dups)[2], ]
# Drop 41 (see the note)
res[res$RubricId==names(dups)[3], ]
# Drop 77 Why resubmit?
res[res$RubricId==names(dups)[4], ]
# Drop 71 ?
res[res$RubricId==names(dups)[5], ]
# Drop 1
res[res$RubricId==names(dups)[6], ]
# Drop 83 ?
res[res$RubricId==names(dups)[7], ]
# Drop 88 ?
res[res$RubricId==names(dups)[8], ]
# Different sections but provided same ID. Actual error. Drop 116.
res[res$RubricId==names(dups)[9], ]
# Drop 37
res[res$RubricId==names(dups)[10], ]
# Drop 93 ?
res[res$RubricId==names(dups)[11], ]
# Drop 92 ?
```
```{r}
id.drop <- c(2, 22, 41, 77, 71, 1, 83, 88, 116, 37, 93, 92)
res <- res %>% filter(!ID %in% id.drop)
```

And trim some variables and format.
```{r }
res <- res %>% select(-Course) %>%
  mutate(
    Section = paste(CID1, CID2, CID3),
    Course = paste(CID1, CID2),
    across(c(ID, Email:Semester, Section:Course), factor)
    )
```

## Merge
Merge the survey data into the D2L.
```{r}
dim(df)
df <- df %>%
  left_join(res %>% select(RubricId, Instructor = Name, Course,
                           `Assessment Name`, Semester,
                           Section, Course), by="RubricId")
dim(df)
```



# Munge Data

Summary of the data:
```{r}
summary(df)
```

What are those missing values?
```{r}
summary(df[is.na(df$Semester), ])
table(df[is.na(df$Semester), 1])
```

Concentrated on the rubric id `113393`. Shall I ask Jon about it?

Anyway, separate them for now.

```{r}
df.na <- df[is.na(df$Semester), ]
df <- df[!is.na(df$Semester), ]
summary(df)
```

## Separate
Data are mixture of assessment and attributes.

```{r}
list.levels <- levels(df$LevelAchieved)
list.levels
```
Separate those two by pattern matching.
```{r}
achievements1 <- c("Unsatisfactory", "Developing", "Basic", "Proficient", "Advanced")
achievements2 <- c("Unacceptable", "Rudimentary", "Fair", "Good", "Excellent")
pttrn <- paste(c(achievements1, achievements2), collapse = "|")

mdf <- df[grepl(pttrn, df$LevelAchieved), ]
sdf <- df[!grepl(pttrn, df$LevelAchieved), ]
mdf$LevelAchieved <- droplevels(mdf$LevelAchieved)
sdf$LevelAchieved <- droplevels(sdf$LevelAchieved)
```

Now this `mdf` only contains rubrics with achievment levels.
```{r}
table(mdf$LevelAchieved)
```


Moreover, standardize levels. As seen in Note 1, those levels can be inconsistent even with the same instructor (e.g. me) across semesters.
```{r}
mdf <- mdf %>% mutate(LevelAchieved = str_extract(mdf$LevelAchieved, pttrn))
names(achievements2) <- achievements1 # Use named list with str_replace_all
mdf$LevelAchieved <- str_replace_all(mdf$LevelAchieved, achievements2)
mdf$LevelAchieved <- ordered(mdf$LevelAchieved, levels = achievements2)

table(mdf$LevelAchieved)
```

## Notes on Levels
Got a note from Beth:

> Some notes:
GW = online (this is true for both undergrad and grad)
>
> For undergrad (note the order from A, B, C, D, F)
> Excellent/advanced + Good/proficient + Basic/Fair = Meets expectation (maybe stacked bar shades of blue? with excellent/advanced being darkest)
> Rudimentary/poor/developing + Unacceptable/unsatisfactory = not met (maybe stacked bar shades of orange or red?)
> 
> For grad
> Excellent/advanced + Good/proficient = Meets expectation
> Basic/Fair + Rudimentary/poor/developing + Unacceptable/unsatisfactory = not met 
> 
> We've got several types of charts
> •	Met/not met (and trends over time)
> •	On-ground/online
> •	Grade trends by faculty member by course number

So, I need to make a distinction between undergrad/grad when it comes to checking the achievement. Totally forgot.

```{r}
mdf <- mdf %>% mutate(
  Met.UND = case_when(is.na(LevelAchieved) ~ "Missing",
    LevelAchieved == "Excellent" | LevelAchieved == "Good" |
      LevelAchieved == "Fair" ~ "Met",
    TRUE ~ "Not Met"),
  Met.GRD = case_when(is.na(LevelAchieved) ~ "Missing",
    LevelAchieved == "Excellent" | LevelAchieved == "Good" ~ "Met",
    TRUE ~ "Not Met")
  )
table(mdf$LevelAchieved, mdf$Met.GRD)
```

## Critrion Names
Criterion names have some strange issues. Some contains a double quotation mark (with escaped). This can be confirmed in the original data. 
Also, some appear to be incomplete, only having learning objective labels.

How can I confirm they are error or not? Check known rubrics? Ask Jon?

```{r}
levels(mdf$Name)
```

At least, it's easy to deal with the quotation mark.
```{r}
mdf$Name <- as.factor(str_remove(mdf$Name, '^"'))
head(levels(mdf$Name))
```

Let's deal with them case by case for now. Then I can find a solution later.


# Inspect Data
Finally, the data is (sufficiently) ready for inspection.
Let's pick a few classes and examine.

## ECO 201
ECO 201 data has been checked in Note 1. However, any disaggregation by criterion was not done.
Apparently, there are quite a bit of variations in criterion wording. Even worse than achievement levels.

```{r}
tdf <- mdf %>% filter(Course == "ECO 201")
tdf <- droplevels(tdf)
table(tdf$Instructor, tdf$Name)
```
## Another class

```{r}
#table(factor(mdf$Course2), mdf$Course)
sdf <- mdf %>% filter(Course2 == "MGT 300")
levels(factor(sdf$`Assessment Name`))
```


```{r}
tdf <- sdf %>% filter(grepl("Hidden", `Assessment Name`))
tdf <- droplevels(tdf)

table(factor(tdf$Name))
table(factor(tdf$`Assessment Name`))
table(tdf$`Assessment Name`, tdf$Course)
```


```{r}
tdf$Name <- str_remove(tdf$Name, '"')
table(factor(tdf$Name))
table(tdf$`Assessment Name`, tdf$Course)
```


```{r}
ggplot(tdf) + geom_bar(aes(LevelAchieved)) + facet_wrap(vars(Name))
```

