---
title: "Note to Inspect Rubric Data 6"
date: 7/6/2020
output:
  html_notebook:
    toc: yes
    toc_float:
      collapsed: yes
    code_folding: hide
  html_document:
    toc: yes
    toc_float:
      collapsed: no
    df_print: paged
    code_folding: hide
    fig_height: 7
    fig_width: 7
---

```{r, echo=FALSE, include=FALSE}
#knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
```

# Objective
Data are mostly cleaned and organized; PLOs are largely matched for Standard 4 reporting; yet, there are several critically missing pieces. 1) Present the outcomes for those which are present and 2) sort out the current situation and follow up with faculty/staff for missing information (i.e. missing data, assessments, and mappings).

# Set up
Import data. Codes are externalized for reuse. As a reference:

- `mdf` or main data frame contains the rubric outcome data merged with the course/assessment information gathered from the survey. Data are cleaned up.
- `non` or non-rubric data frame is separated from the same data source as the rubric information of `mdf`. It contains the instructor's assessments of outcomes at course level. Data are cleaned up.
- `past` data frame contains the assessment outcome data from the past.
- `rowmap` data frame summarizes the mapping between PLOs and rubric rows.
```{r}
source('read.R')
source('munge.R')
```

Those scripts have been updated to use the *edited* version of the survey result data. See Note 5 for details.

Given that change, the Notebooks 1-5 are completely outdated.

# PLO Measures for Standard 4

## Overview
For Standard 4, we only need a rather small subset of the assessments available. Produce the summary of outcomes in the context of historical changes. 

- ACBSP requires 3-5 data points, so make sure to have sufficient numbers.
- ACBSP requires graphs with sample sizes.
- Nuventive requires numbers. Produce data tables along with the graphs.

Once Standard 4 is done, we can discuss weakness/shortcomings and strength/improvements in our program, then look at other courses - including the ones at an earlier stage of each program - to find *opportunities for improvement* and *close the loop*. That is, we can get to **Standard 6** analysis.

## Summarize Outcomes
Rubric outcome data are collected at individual level. Take average over `Course` level for each assignment. All the inconsistencies have been dealt with.
```{r}
# Undergrad focus for now
tbl1 <- mdf %>% filter(str_detect(Name, "Major|Minor", negate = TRUE)) %>%
  group_by(Course, Assessment, Name, PLO) %>%
  summarise(Met = mean(Met.UND.bin), Met.GRD = mean(Met.GRD.bin), n = n())
```

Non-rubric data are collected at `Section` level and as shares of students who achieved goals. Use the class size as a weight to have the proper aggregation. Moreover, keep the `PLO` column for identifying apparently-identical assessments (e.g. different parts of exams).
```{r}
tbl2 <- non %>%
  group_by(Course, Assessment, PLO) %>%
  summarise(Met = weighted.mean(x = np/n, w = n, na.rm = TRUE),
            Met.GRD = Met,
            n = sum(n, na.rm = TRUE), Name = "NA")
```

Now the outcomes are summarized in a compatible way for both rubric-based and non rubric-based assessments.
```{r}
tbl3 <- tbl1 %>% bind_rows(tbl2)
```

## Prepare
```{r}
get_outcome <- function(plotag, rrow, program, plo, grad = FALSE){
  if(is.na(plotag)){return(NA)}
  if(grad){
    tbl3 %>% filter(PLO == plotag, str_detect(Name, rrow)) %>% ungroup() %>% 
      summarize(Met = mean(Met.GRD), n = min(n)) %>%
      mutate(Program = program, PLO = plo)
  }
  else{
    tbl3 %>% filter(PLO == plotag, str_detect(Name, rrow)) %>% ungroup() %>% 
      summarize(Met = mean(Met), n = min(n)) %>%
      mutate(Program = program, PLO = plo)
  }
}
#get_outcome(plotag = "BUS 5, BUS 6", rrow = "5[a|b|c|d]",
#            program = "Business Core", plo = 5)
```

```{r}
#levels(factor(tbl3$PLO))
list.plotags <- list("Accounting" = c("ACC 1", "ACC 2", NA, "ACC 4"),
          "Business Core" = c(NA, "BUS 2", "BUS 3, BUS 5, BUS 6", "BUS 4, BUS 9",
                              "BUS 3, BUS 5, BUS 6", "BUS 3, BUS 5, BUS 6",
                              "BUS 7, BUS 8", "BUS 7, BUS 8", "BUS 4, BUS 9",
                              "BUS 10"),
          "Economics" = c("ECO 2"),
          "Human Resources Management" = paste("HRM", 1:4),
          "Management" = c(rep("MGT 1, MGT 2, MGT 3", 3), "MGT 4"),
          "MBA" = c(paste("MBA", 1:4), NA, paste("MBA", 6:8))
          )
list.rrows <- list(
  "Accounting" = rep("NA", 4),
  "Business Core" = c(NA, "Plo2", "Plo3", "Plo4", "5[a|b|c|d]", "6[e|f|g]",
                      "Plo7", "Plo8", "Plo9", ".*"),
  "Economics" = c(".*"),
  "Human Resources Management" = c("Organizational Types",
           "(Organizational Types)|(Organizational Strategy)",
           "Hr Law", ".*"),
  "Management" = c("Plo1", "Plo5", "Plo7", ".*"),
  "MBA" = rep(".*", 8)
  )
# MIS, MKT
```

```{r}
get_outcomes <- function(program, grad = FALSE){
  # Wrapper to return a combined results for each program
  lres <- list()
  plotags <- list.plotags[[program]]
  rrows <- list.rrows[[program]]
  for(i in 1:length(plotags)){
    lres[[i]] <- get_outcome(plotags[i], rrows[i], program, i, grad)
  }
  lres
}

merge_outcomes <- function(lres, program){
  # Wrapper function to merge with the historical assessment results
  lres <- lres[!is.na(lres)] # Missing assessment returns NA
  x <- bind_rows(lres)
  x <- x %>% ungroup() %>%
    transmute(`Learning Objective Number` = PLO,
              `Academic Year` = rep(2019, nrow(x)),
              `Outcome` = Met, `Sample Size` = n )
  
  y <- past %>%
    filter(Program == program,
           str_detect(`Assessment Type`, "(Internal$)|(Internal Formative)"),
           str_detect(Source, "2020")) %>% 
    select(`Learning Objective Number`, `Academic Year`,
           Outcome, `Sample Size`)
  out <- bind_rows(x, y)
  out %>% arrange(`Learning Objective Number`, `Academic Year`)
}

getmerge_outcomes <- function(program, grad = FALSE){
  lres <- get_outcomes(program, grad)
  merge_outcomes(lres, program)
}

#getmerge_outcomes("Accounting")
#past %>% filter(Program == "MBA", str_detect(`Assessment Type`, "(Internal$)|(Internal Formative)"))
```

```{r}
make_graph <- function(df.out, program){
  title <- paste0(program, ", Prevalence of Achievments Over Academic Years, by PLO")
  caption <- "Grey number represents sample size.\nFor 2019, minimum sample size is used if prevalence is computed from multiple criteria."
  
  p <- ggplot(df.out, aes(x = `Academic Year`, y = Outcome,
                          group = `Learning Objective Number`)) +
    geom_line(na.rm = TRUE) +
    geom_point(aes(color = Outcome > goal), na.rm = TRUE) +
    scale_colour_manual(values = setNames(c('blue','red'),c(T, F))) +
    geom_text(aes(`Academic Year`, 0.5, label = round(`Sample Size`, 0)),
              alpha = 0.4, na.rm = TRUE) +
    geom_hline(aes(yintercept = goal), alpha = 0.5) +
    scale_y_continuous(labels=scales::percent)
  p + facet_wrap(vars(`Learning Objective Number`)) +
    theme_minimal() +
    labs(title = title, caption = caption) +
    theme(axis.title = element_blank(),
          text = element_text(family = "serif"),
          panel.grid.minor.x = element_blank(),
          legend.position = "none")
}
```

## Follow Up

```{r}
survey %>% filter(`Follow up` != "NA")
```

- [ ] Fatma El-Hamidi, Spring 2020, BUS 381-002, Final Exam, No assessment for an exam?
- [x] Beth, Fall 2019, BUS 499-GW1, Simulation After Action Report, Mapped to anything? > **Same as GoVenture AAR** ...Fixed.
- [x] Dave & Paul R. Ask Beth? BUS 799, "Chapter Case Study" "Comprehensive Project". Supposed to be exam scores? >> Waiting for Stephanie.
- [x] Chris? FIN 301. "Ratio Calculation", "Ratio Interpretation Signature Assignment #3", "NPV Calculation", "Moral Hazard" (Ed inputs); FIN 301 "Ration Analysis - Rich Uncle Scenario" (Chris entered); "Signature Assignment 3", "Signature Assignment 2" (Nan entered). >> Nan's response clarified most. Helpful to know that the Signature Assignment 3 (Capital Budgeting) was discontinued. No wonder I can't have a consistent matching.
- [x] To begin with, Finance program should use FIN 302 Capital Budgeting for assessment of both 1 and 2. Likely outdated? Ask Nan. >> Okay, **FIN 301 is not used for proram assessment.** I need FIN 302 data for assessment. Remove all FIN 301 plo tags. ...Done.
- [ ] Rich MKT 300. Assess PLO 1-10… while only 1-3 available?
FIN 711 for MBA 3, missing. ...Wait. It should be from 401. Eric Freeman taught and answered. >>

I'm so confused. I suppose those files in 2019-20 folder are updated versions. However, worksheets contradict with the overview sheet. I don't know what data those sheets refer to.

## Outcomes
### Accounting

```{r}
acc <- getmerge_outcomes("Accounting")
knitr::kable(acc, dig=2)
```


```{r}
ref <- tibble(`Learning Objective Number` = 1:4, goal = rep(0.7, 4))
acc <- acc %>% left_join(ref, by = "Learning Objective Number")
make_graph(acc, "Accounting")
```

```{r}
x <- rowmap %>% filter(Program == "Accounting") %>%
  discard(~all(is.na(.x))) %>% map_df(~.x) %>% 
  select(-c(Program, Goal, `Last Checked`))
knitr::kable(x)
```

### Business Core
```{r}
bus <- getmerge_outcomes("Business Core")
knitr::kable(bus, dig=2)
```


```{r}
ref <- tibble(`Learning Objective Number` = 1:10, goal = c(rep(0.7, 8), 0.9, 0.7))
bus <- bus %>% left_join(ref, by = "Learning Objective Number")
make_graph(bus, "Business Core")
```


```{r}
x <- rowmap %>% filter(Program == "Business Core") %>%
  discard(~all(is.na(.x))) %>% map_df(~.x) %>% 
  select(-c(Program, Goal, `Last Checked`))
knitr::kable(x)
```

### Economics
Only one PLO is identified yet.
```{r}
eco <- getmerge_outcomes("Economics")
knitr::kable(eco, dig=2)
```


### Finance
All the assessment from FIN 302. Waiting for the data from Jon Kallis.

### Human Resource Management
```{r}
hrm <- getmerge_outcomes("Human Resources Management")
knitr::kable(hrm, dig=2)
```


```{r}
ref <- tibble(`Learning Objective Number` = 1:4, goal = rep(0.7, 4))
hrm <- hrm %>% left_join(ref, by = "Learning Objective Number")
make_graph(hrm, "Human Resources Management")
```


```{r}
x <- rowmap %>% filter(Program == "Human Resources Management") %>%
  discard(~all(is.na(.x))) %>% map_df(~.x) %>% 
  select(-c(Program, Goal, `Last Checked`))
knitr::kable(x)
```

### Management
```{r}
mgt <- getmerge_outcomes("Management")
knitr::kable(mgt, dig=2)
```

```{r}
ref <- tibble(`Learning Objective Number` = 1:4, goal = rep(0.7, 4))
mgt <- mgt %>% left_join(ref, by = "Learning Objective Number")
make_graph(mgt, "Management")
```

```{r}
x <- rowmap %>% filter(Program == "Management") %>%
  discard(~all(is.na(.x))) %>% map_df(~.x) %>% 
  select(-c(Program, Goal, `Last Checked`))
knitr::kable(x)
```

### Marketing
All the assessment from MKT 401. Eric Freeman has one rubric outcome.
```{r}
tbl3 %>% filter(Course == "MKT 401") %>% ungroup() %>% select(Assessment, Name, n) %>% knitr::kable()
```

```{r}
mdf %>% filter(Course == "MKT 401") %>% group_by(Section, Name) %>% summarise(n = n())
```

```{r}
x <- rowmap %>% filter(Program == "Marketing") %>%
  discard(~all(is.na(.x))) %>% map_df(~.x) %>% 
  select(-c(Program, Goal, `Last Checked`))
knitr::kable(x)
```

- [x] Ask Rich?

### MBA
Course for MBA PLO5 was not offered this term.


```{r}
mba <- getmerge_outcomes("MBA", grad = TRUE)
knitr::kable(mba, dig=2)
```

```{r}
ref <- tibble(`Learning Objective Number` = 1:8, goal = rep(0.85, 8))
mba <- mba %>% left_join(ref, by = "Learning Objective Number")
make_graph(mba, "MBA")
```

```{r}
x <- rowmap %>% filter(Program == "MBA") %>%
  discard(~all(is.na(.x))) %>% map_df(~.x) %>% 
  select(-c(Program, Goal, `Last Checked`))
knitr::kable(x)
```


# Next
