---
title: "Note to Inspect Rubric Data 5"
date: 7/3/2020
output:
  html_notebook:
    toc: yes
    toc_float:
      collapsed: yes
    code_folding: hide
  html_document:
    toc: yes
    toc_float:
      collapsed: no
    df_print: paged
    code_folding: hide
---

```{r, echo=FALSE, include=FALSE}
#knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
```

# Objective
Data are mostly cleaned and organized; PLOs are largely matched for Standard 4 reporting; yet, there are several critically missing pieces. 1) Present the outcomes for those which are present and 2) sort out the current situation and follow up with faculty/staff for missing information (i.e. missing data, assessments, and mappings).

# Set up
Import data. Codes are externalized for reuse. As a reference:
- `mdf` or main data frame contains the rubric outcome data merged with the course/assessment information gathered from the survey. Data are mostly cleaned up.
- `past` data frame contains the assessment outcome data from the past.
- `non` data frame contains the AY2019 assessments without rubrics.
```{r}
source('read.R')
# ToDo: Avoid use of side-effects. Save and reload. Merge this step with top chunk.
source('munge.R')
```

In this document, begin some refactoring for convenience in the future. Document them and apply into the source files above, when moving on to the next iteration.

## Non-rubric Outcomes Clean up
First, distinguish course and section.
```{r}
non <- non %>%
  mutate(Section = factor(Course),
         Course = factor(str_sub(Course, 1, 7)))
```

Assessment Names are not standardized and subject to aggregation errors. 
```{r}
levels(factor(non$`Assessment Name`))
```

Assessment names:
```{r}
tbl <- non %>% group_by(Course, `Assessment Name`) %>% summarize(n = n())
knitr::kable(tbl)
```

```{r, eval=FALSE}
non %>% filter(str_detect(`Assessment Name`, "Information Literacy")) # into this

non %>% filter(str_detect(`Assessment Name`, "Exam")) %>% select(Section, `Assessment Name`, `PLO Mixed`) # List up?
# Same "exam" can refer to different parts. Check PLOs.

non %>% filter(Course == "BUS 242", str_detect(`Assessment Name`, "signature assignment")) # Into Singature Assignment

non %>% filter(Course == "BUS 381") # ? Signature Assignment = Final Project, but multiple objectives?
non %>% filter(Course == "BUS 381") %>% select(Section, `Assessment Name`, `PLO Mixed`) # LO1-3,5,8 are separate in 002. Aggregate to be consistent with others?
non %>% filter(Course == "BUS 381", str_detect(`Assessment Name`, "(Final Project)|(Signature Assignment)")) # Into "Signature Assignment"/

non %>% filter(Course == "FIN 301") # 1: Ratio data ~ Sig 1, 2: capital budgeting, 3:Ethics ~ Sig 4, "Rich Uncle" combines 1 & 2; 2019 Fall different? ... Need to ask.

non %>% filter(Course == "MGT 300")
non %>% filter(Course == "MGT 300", str_detect(`Assessment Name`, "Burt's Bees")) # Into Burt's Bees
non %>% filter(Course == "MIS 201") # Mark Kjellander inconsistent with Adnan's? With Final Exam question and ALL LO ... Leave as is and skip. Meanwhile, ask Adnan for clarification
```
```{r}
# Test:
#course1 <- "BUS 381"
#name1 <- "(Final Project)|(Signature Assignment)"
#pattern1 <- "(.*Final Project.*)|(.*Signature Assignment.*)"
#name2 <- "Signature Assignment"
#
#non %>% filter(Course == course1, str_detect(`Assessment Name`, name1)) %>% transmute(`Assessment Name`, New = str_replace_all(`Assessment Name`, pattern1, name2))

pttrn.bus771 <- c(".*Information Literacy.*" = "Information Literacy",
                  ".*Exam.*" = "Exam")
pttrn.bus242 <- c("signature assignment.*" = "Signature Assignment")
pttrn.bus381 <- c("(.*Final Project.*)|(.*Signature Assignment.*)" = "Signature Assignment")
pttrn.mgt300.2 <- c("Burt's Bees.*" = "Burt's Bees")
pttrn <- c(pttrn.bus771, pttrn.bus242, pttrn.bus381, pttrn.mgt300.2)

non <- non %>% mutate(`Assessment Name` = str_replace_all(`Assessment Name`, pttrn))
table(non$`Assessment Name`)
```

PLOs:
```{r}
# Standardize cases and extra spaces
non <- non %>% mutate(`PLO Mixed` =
                        str_replace_all(str_to_upper(`PLO Mixed`), "\\s\\s", " "))
table(non$`PLO Mixed`)
```

Lastly, convert variable types and compute the proporiton of students who passed the goal.
```{r}
non <- non %>% mutate(Instructor = factor(Instructor),
                      Semester = factor(Semester),
                      Program = factor(Program),
                      Met = pass_n / n)
summary(non)
```


## Mapping
Excel files under `2. Assessment Plan` folder in SharePoint are good for *developing assessment plans* but hard to refer back. Use the "database" file `/Data/Assessment Data Main.xlsx` for *maintenance*.

Specify the "Main" worksheet while reading the file in `read.R` (i.e. modify the existing line) and "Mapping" worksheet for the new info (i.e. add a new line). The mapping is stored in `map` object.

# PLO Measures for Standard 4

## Overview
For Standard 4, we only need a rather small subset of the assessments available. Produce the summary of outcomes in the context of historical changes. 

- ACBSP requires 3-5 data points, so make sure to have sufficient numbers.
- ACBSP requires graphs with sample sizes.
- Nuventive requires numbers. Produce data tables along with the graphs.

Once Standard 4 is done, we can discuss weakness/shortcomings and strength/improvements in our program, then look at other courses - including the ones at an earlier stage of each program - to find *opportunities for improvement* and *close the loop*. That is, we can get to **Standard 6** analysis.

## Summarize Outcomes
Rubric outcome data are collected at individual level. Take average over `Course` level for each assignment. All the inconsistencies have been dealt with.
```{r}
# Undergrad focus for now
tbl1 <- mdf %>% filter(str_detect(Name, "Major|Minor", negate = TRUE)) %>%
  group_by(Course, `Assessment Name`, Name) %>%
  summarise(Met = mean(Met.UND.bin), n = n())
```

Non-rubric data are collected at `Section` level and as shares of students who achieved goals. Use the class size as a weight to have the proper aggregation. Moreover, keep the `PLO Mixed` column for identifying apparently-identical assessments (e.g. different parts of exams).
```{r}
tbl2 <- non %>%
  group_by(Course, `Assessment Name`, `PLO Mixed`) %>%
  summarise(Met = weighted.mean(x = pass_n/n, w = n, na.rm = TRUE),
            n = sum(n, na.rm = TRUE))
#non %>% filter(Course == "BUS 381")
#non %>% filter(Course == "FIN 301")
```

Lastly, the mapping between PLOs and rubric rows, where available, can be used to pick up relevant information.
```{r}
# map is taken by purr. Rename it...
mapping <- map
# Replace text NA into na
mapping <- mapping %>% mutate(across(where(is.character), na_if, "NA"))
```

### Mapping Usage?
Now, when exact match of assessment names are rare. How shall I automte this?

List up PLOs for a program.
```{r}
x <- mapping %>% filter(Program == "Accounting") %>%
  discard(~all(is.na(.x))) %>% map_df(~.x) %>% 
  select(-c(Program, Goal, `Last Checked`))
knitr::kable(x)
```

Extract each PLO.
```{r}
mapping[1, ]
```

If assessment names are uniquely identified, I can merge `mdf` and `non` with `mapping` and filter results. However, that's not the case at all. Instead, manually select rows (as in the previous note), but use the assessment names taken from the `mapping` ... with modification.

Treat `PLO Mixed` as if they are rubric rows and merge the data frames.
```{r}
names(tbl1); names(tbl2)
tbl2 <- tbl2 %>% rename(Name = `PLO Mixed`)
tbl3 <- tbl1 %>% bind_rows(tbl2)
summary(tbl3)
```

Now, try to find patterns?
```{r}
mapping %>% filter(Program == "Accounting") %>%
  discard(~all(is.na(.x))) %>% map_df(~.x) %>% 
  select(-c(Program, Goal, `Last Checked`))
x <- tbl3 %>% filter(Course == "ACC 331", `Assessment Name` == "Exam", Name == "ACCOUNTING LO 1")
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 2)
tbl3 %>% filter(Course == "ACC 331", `Assessment Name` == "Exam", Name == "ACCOUNTING LO 2")
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 3)
tbl3 %>% filter(Course == "ACC 441", `Assessment Name` == "Exam", Name == "ACCOUNTING LO 4")
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 4)

mapping %>% filter(Program == "Business Core") %>%
  discard(~all(is.na(.x))) %>% map_df(~.x) %>% 
  select(-c(Program, Goal, `Last Checked`))
tbl3 %>% filter(Course == "BUS 499")
x <- tbl3 %>% filter(Course == "BUS 499", `Assessment Name` == "Annotated Bibliography", str_detect(Name, "Plo2"))
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 2)
x <- tbl3 %>% filter(Course == "BUS 499", `Assessment Name` == "Company Profile", str_detect(Name, "Plo3"))
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 3)
x <- tbl3 %>% filter(Course == "BUS 499", `Assessment Name` == "Goventure Aar", str_detect(Name, "Plo4"))
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 4)
x <- tbl3 %>% filter(Course == "BUS 499", `Assessment Name` == "Company Profile", str_detect(Name, "5[a|b|c|d]"))
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 5)
x <- tbl3 %>% filter(Course == "BUS 499", `Assessment Name` == "Company Profile", str_detect(Name, "6[e|f|g]"))
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 6)
x <- tbl3 %>% filter(Course == "BUS 499", `Assessment Name` == "Ethics Case Paper", str_detect(Name, "Plo7"))
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 7)
x <- tbl3 %>% filter(Course == "BUS 499", `Assessment Name` == "Ethics Case Paper", str_detect(Name, "Plo8"))
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 8)
x <- tbl3 %>% filter(Course == "BUS 499", `Assessment Name` == "Goventure Aar", str_detect(Name, "Plo9"))
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 9)
x <- tbl3 %>% filter(Course == "BUS 499", `Assessment Name` == "Development Plan", str_detect(Name, ".*"))
x %>% summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = 10)

```

I still need to feed course and assessment name, but the rest can be generalized.
```{r}
cname <- "BUS 499"
aname <- "Annotated Bibliography"
oname <- "Plo2"
plo <- 2
tbl3 %>% filter(Course == cname, `Assessment Name` == aname,
                str_detect(Name, oname)) %>% 
  summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = plo)
```

So, make a simple wrapper.
```{r}
cname <- "BUS 499"
aname <- "Annotated Bibliography"
oname <- "Plo2"
plo <- 2
get_outcome <- function(cname, aname, oname, plo){
  if(is.na(cname)){return(NA)}
  tbl3 %>% filter(Course == cname, `Assessment Name` == aname,
                  str_detect(Name, oname)) %>% 
    summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = plo)
}
get_outcome(cname, aname, oname, plo)
```

And, I want a table and a graph for each program. Make a list as before.
```{r}
pname <- "Accounting"
cnames <- c("ACC 331", "ACC 331", "ACC 441")
anames <- c("Exam", "Exam", "Exam")
onames <- c("ACCOUNTING LO 1", "ACCOUNTING LO 2", "ACCOUNTING LO 4")
plos <- c(1, 2, 4)

lres <- list()
i <- 1
lres[[i]] <- get_outcome(cnames[i], anames[i], onames[i], plos[i])
i <- i + 1
lres[[i]] <- get_outcome(cnames[i], anames[i], onames[i], plos[i])
i <- i + 1
lres[[i]] <- get_outcome(cnames[i], anames[i], onames[i], plos[i])
```

Wrap it.
```{r}
pname <- "Accounting"
cnames <- c("ACC 331", "ACC 331", NA, "ACC 441")
anames <- c("Exam", "Exam", NA, "Exam")
onames <- c("ACCOUNTING LO 1", "ACCOUNTING LO 2", NA, "ACCOUNTING LO 4")
plos <- 1:4

get_outcomes <- function(pname, cnames, anames, onames, plos){
  lres <- list()
  for(i in 1:length(plos)){
    lres[[i]] <- get_outcome(cnames[i], anames[i], onames[i], plos[i])
  }
  lres
}
get_outcomes(pname, cnames, anames, onames, plos)
```

Put the list into a table and a graph.
```{r}
lres <- get_outcomes(pname, cnames, anames, onames, plos)

get_output <- function(pname, lres){
  lres <- lres[!is.na(lres)]
  x <- bind_rows(lres)
  x <- x %>% ungroup() %>% 
    transmute(`Academic Year` = rep(2019, nrow(x)),
              `Learning Objective Number` = as.numeric(PLO),
              `Outcome` = mean, `Sample Size` = n )
  y <- past %>%
    filter(Program == pname, `Assessment Type` == "Internal",
           str_detect(Source, "2020")) %>% 
    select(`Academic Year`, `Learning Objective Number`, Outcome, `Sample Size`)
  out <- bind_rows(x, y)
  
  title <- paste0(pname, ", Prevalence of Achievments Over Academic Years, by PLO")
  caption <- "Grey number represents sample size.\nFor 2019, minimum sample size is used if prevalence is computed from multiple criteria."
  p <- ggplot(out,
         aes(`Academic Year`, Outcome, group = `Learning Objective Number`)) +
    geom_line(na.rm = TRUE) +
    geom_point(aes(color = Outcome > 0.7), na.rm = TRUE) +
    scale_colour_manual(values = setNames(c('blue','red'),c(T, F))) +
    geom_text(aes(`Academic Year`, 0.5, label = round(`Sample Size`, 0)),
              alpha = 0.4, na.rm = TRUE) +
    geom_hline(yintercept = 0.7, color = "red") +
    scale_y_continuous(labels=scales::percent) +
    facet_wrap(vars(`Learning Objective Number`)) +
    theme_minimal() +
    labs(title = title, caption = caption) +
    theme(axis.title = element_blank(),
          text = element_text(family = "serif"),
          panel.grid.minor.x = element_blank(),
          legend.position = "none")
    
  list(out, p)
}

out <- get_output("Accounting", lres)
knitr::kable(out[[1]], dig=2)
print(out[[2]])
```

More.
```{r}
clist <- list("Accounting" = c("ACC 331", "ACC 331", "ACC 441"),
           "Business Core" = rep("BUS 499", 10))
alist <- list("Accounting" = c("Exam", "Exam", "Exam"),
              "Business Core" = c("Annotated Bibliography", "Company Profile",
                                  "Goventure Aar", "Company Profile",
                                  "Company Profile", "Ethics Case Paper",
                                  "Ethics Case Paper", "Goventure Aar",
                                  "Development Plan"))
olist <- list("Accounting" = c("ACCOUNTING LO 1", "ACCOUNTING LO 2",
                               "ACCOUNTING LO 4"),
           "Business Core" = c("Plo2", "Plo3", "Plo4", "5[a|b|c|d]", "6[e|f|g]",
                               "Plo7", "Plo8", "Plo9", ".*"))
plist <- list("Accounting" = c(1, 2, 4),
              "Business Core" = 2:10)


pname <- "Accounting"
get_outcomes(pname, clist[[pname]], alist[[pname]], olist[[pname]], plist[[pname]])
pname <- "Business Core"
lres <- get_outcomes(pname, clist[[pname]], alist[[pname]], olist[[pname]], plist[[pname]])

out <- get_output(pname, lres)
knitr::kable(out[[1]], dig=2)
print(out[[2]])
```

Good.

Manual entry of the assessment information is really tedious and the wrapper functions only save a small amount of work. However, it highlights what I need to have in the future. If I can refer to a data frame for course, assessment names, and rubric rows by simply specifying a program name, then this process is entirely automatic from data.

I might as well standardize the input files even more... Anyway, now I just need to have a full list of those identifiers.

### Thoughts
Probably I can be more relaxed about preserving the data sources. After all, the important one is D2L outcome data. Other things are more or less "manually handled" anyway.

Part of the reason is those files are really really small (~150 or so rows). If I edit the survey data - I did that anyway for non-rubric data - to have standardized course names and assessment names, I can skip a fair number of steps. Moreover, hard-coded mapping in scripts is no better than manually handled spreadsheet...

Now, rubric rows are different... They are only available in D2L outcome data. 1) it's much larger (>18k rows) and 2) contents are not explicitly entered in survey. Check each from data and edit by substitution make more sense.
```{r}
clist <- list(
  "Accounting" = c("ACC 331", "ACC 331", NA, "ACC 441"),
  "Business Core" = c(NA, rep("BUS 499", 10)),
  "Economics" = c("ECO 302"),
  "HR" = rep("HR 400", 4),
  "Management" = rep("BUS 345", 4),
  "MBA" = c("ACC 711", "ECO 716", "FIN 711", "HR 711", NA, "MKT 711", NA, "BUS 771")
  )
alist <- list(
  "Accounting" = c("Exam", "Exam", NA, "Exam"),
  "Business Core" = c(NA, "Annotated Bibliography", "Company Profile",
                      "Goventure Aar", "Company Profile",
                      "Company Profile", "Ethics Case Paper",
                      "Ethics Case Paper", "Goventure Aar",
                      "Development Plan"),
  "Economics" = c("Exam"),
  "HR" = c("Paper #1", "Simulation Paper #2", 
                                  "Simulation Paper 3", "Peer evaluations"),
  "Management" = c("Ethics Final Paper", "Ethics Final Paper", "Ethics Final Paper", "Ethics Reflection"),
  "MBA" = c("Managerial Accounting Research", "Exam", "Exam", "Exam", "Exam", "Exam", "Exam", "Exam")
  )
olist <- list(
  "Accounting" = c("ACCOUNTING LO 1", "ACCOUNTING LO 2", NA, "ACCOUNTING LO 4"),
  "Business Core" = c(NA, "Plo2", "Plo3", "Plo4", "5[a|b|c|d]", "6[e|f|g]",
                      "Plo7", "Plo8", "Plo9", ".*"),
  "Economics" = c(".*"),
  "HR" = c("Organizational Types",
                                  "(Organizational Types)|(Organizational Strategy)",
                                  "Hr Law", ".*"),
  "Management" = c("Plo1", "Plo2", "Plo7", ".*"),
  "MBA" = rep(".*", 8)
  )
plist <- list("Accounting" = 1:4,
              "Business Core" = 1:10,
              "Economics" = c(2),
              "HR" = 1:4,
              "Management" = 1:4,
              "MBA" = 1:8
              )
```

```{r}
pname <- "Economics"
lres <- get_outcomes(pname, clist[[pname]], alist[[pname]], olist[[pname]], plist[[pname]])

out <- get_output(pname, lres)
knitr::kable(out[[1]], dig=2)
print(out[[2]])

```


```{r}
pname <- "HR"
lres <- get_outcomes(pname, clist[[pname]], alist[[pname]], olist[[pname]], plist[[pname]])

out <- get_output(pname, lres)
knitr::kable(out[[1]], dig=2)
print(out[[2]])
```

```{r}
pname <- "Management"
lres <- get_outcomes(pname, clist[[pname]], alist[[pname]], olist[[pname]], plist[[pname]])

out <- get_output(pname, lres)
knitr::kable(out[[1]], dig=2)
print(out[[2]])
```

```{r}
pname <- "MBA"
lres <- get_outcomes(pname, clist[[pname]], alist[[pname]], olist[[pname]], plist[[pname]])
out <- get_output(pname, lres)
knitr::kable(out[[1]], dig=2)
print(out[[2]])

past %>% filter(Program == "MBA")
# Internal Formative
# Threshold differs
```


# Data Edit
Created a new Excel file with edited input data.

```{r}
fn <- "data/Assessment Survey Responses.xlsx"
survey <- read_excel(fn, "Edited")
head(survey)
```

I can use the non-rubric data from this, but they are not cleaned yet. Filter them out.
```{r}
survey2 <- survey %>%
  filter(`I graded this assessment using a rubric on D2L.` == "Yes",
         !Drop)
head(survey2)
```

```{r}
levels(factor(survey2$Course))
```

```{r}
levels(factor(survey2$PLO))
```

```{r}
levels(factor(survey2$Assessment))
```

Much cleaner!

Also, some notes there.
```{r}
levels(factor(survey2$`Follow up`))
```

After having learned about the data, it was easy to edit the assessment names. The ability to view multiple rows at once helped me as well, taking advantage of comments.

Now, if I use this file, then I can skip `drop-entries` and `clean course` sections of `read.R` and `clean-assessment` of `munge.R`.

## Update Scripts
Let's give it a try:
```{r}
library(tidyverse)
library(readxl)

## ---- import-d2l ----
fn <- "data/Rubrics.xlsx"
df <- read_xlsx(fn) %>%
  mutate(across(c(RubricId:Name, LevelAchieved), factor),
         IsScoreOverridden = (IsScoreOverridden == "True"))
```


```{r}
## ---- import-survey ----
fn <- "data/Assessment Survey Responses.xlsx"
survey <- read_excel(fn, "Edited")
qs <- names(survey)
#cat(str_sub(qs, 1, 8), sep = "\n")
# Not unique... yet
nms <- c("ID" = "ID",
         "Drop" = "Drop",
         "Start ti" = "Start",
         "Completi" = "Complete", 
         "Email" = "Email",
         "Name" = "Instructor",
         "In which" = "Semester",
         "Course A" = "Course.Section.Original",
         "Course" = "Course",
         "Section" = "Section",
         "What is " = "Assessment.Original",
         "Assessme" = "Assessment",
         "Follow u" = "Follow up",
         "I graded" = "Rubric",
         "Copy and" = "URL",
         "Analysis" = "Analysis.Rubric",
         "Action f" = "Action.Rubric",
         "What is " = "PLO.Original",
         "PLO" = "PLO",
         "What is " = "n.original",
         "n" = "n",
         "If this " = "np.original",
         "np" = "np",
         "Analysis" = "Analysis.Non.Rubric",
         "Action f" = "Action.Non.Rubric")
names(survey) <- nms

# Non rubric data are not relevant for D2L output data
non <- survey %>%
  filter(Rubric == "No", !Drop) %>%  select(-c(URL:Action.Rubric))
survey <- survey %>%
  filter(Rubric == "Yes", !Drop) %>%  select(ID:PLO)

```

```{r}
## ---- extract-rubricid ----
x <- str_extract_all(survey$URL, "rubricId=[0-9]{6}", simplify=TRUE)
survey$RubricId <- factor(str_extract_all(x, "[0-9]{6}", simplify=TRUE))
```


```{r}
tbl <- table(survey$RubricId)
dups <- tbl[tbl > 1]
dups
res[res$RubricId==names(dups)[1], ]
# Drop 22
res[res$RubricId==names(dups)[2], ]
# Modify 41
res[res$RubricId==names(dups)[3], ]
# Drop 66 resubmit?
res[res$RubricId==names(dups)[4], ]
# Drop 65 ?
res[res$RubricId==names(dups)[5], ]
# Drop 61 ?
res[res$RubricId==names(dups)[6], ]
# Drop 62 ?
res[res$RubricId==names(dups)[7], ]
# Drop 114 ?
res[res$RubricId==names(dups)[8], ]
# Different sections but provided same ID. Actual error. Drop 37.
res[res$RubricId==names(dups)[9], ]
# Drop 64 ?
res[res$RubricId==names(dups)[10], ]
# Drop 63 ?

# Double check comments

id.drop <- c(22, 66, 65, 61, 62, 114, 37, 64, 63)
df2 <- survey %>% filter(!ID %in% id.drop)
head(df2)
```



```{r}
## ---- merge ----
names(df2)
dim(df)
mdf <- df %>%
  left_join(df2 %>%
              select(RubricId, Instructor, Semester,
                     Course, Section, Course.Section.Original,
                     Assessment, Assessment.Original,
                     Rubric, PLO.Original, PLO), by="RubricId")
dim(mdf)
```


```{r}
## ---- import supplementary ----
past <- read_excel("data/Assessment Data Main.xlsx", sheet = "Main")
map <- read_excel("data/Assessment Data Main.xlsx", sheet = "Mapping")
#non <- read_excel("data/Non Rubric Data.xlsx")
#non <- non %>% transmute(
#  Instructor = Name,
#  Semester = `In which semester is this course?`,
#  Course = paste(Program, Course, Section),
#  `Assessment Name` = `What is the name of the assessment you used? (e.g., International Trade Case Study, Final Exam Question 3, etc.)`,
#  `Program`, `PLO Mixed`=PLO,
#  n = `What is the total number of students that completed the assessment tool for your second learning objective?`,
#  pass_n = `If this is an undergraduate assessment, how many students achieved a rubric level of "basic" or scored 70% or better on the assessment?  If this is an MBA formative assessment, how many students s...`,
#  Interpretation = `Analysis/Interpretation of Results for your learning objective: Briefly answer the question, What do your assessment data tell us?`,
#  Action = `Action for improvement: Briefly explain how you will use the assessment results to make improvements to your course or curriculum.2`)
```


Then, `munge`. Get rid of all of the assessment name editing codes.
```{r}
pttrn.eco201.n <- c("^Arguments For Protection$"="Arguments For Protectionism",
                    "^Citations$"="Citations/References",
                    "^Structure$"="Structure/Clarity",
                    "^Winners/Losers$"="Winners And Losers",
                    "^Writing: Citations$"="Writing: Citations/References")
pttrn.eco202.n <- 
  c("^Data Collection$" = "Part 1: Data Collection",
    "^Time-Series Graphs$" = "Part 1: Time Series Plots",
    "^Explain Variable Movements$" = "Part 2: Explain Variable Movements",
    "^Short-Run And Long-Run Perspectives$" = "Part 2: Short-Run And Long-Run Perspectives",
    "^Compare And Contrast$" = "Part 2: Compare And Contrast",
    "^Citations$" = "Writing: Citations",
    "^Grammar$" = "Writing: Grammar",
    "^Structure$" = "Writing: Structure")
pttrn.name <- c(pttrn.eco202.n, pttrn.eco201.n)

mdf <- mdf %>%
  mutate(Name = str_to_title(str_remove(mdf$Name, '^"')),
         Name = str_replace_all(Name, pttrn.name))
summary(mdf)
```

The rest encounters no change because it is all about D2L outcome data, which are not altered by the change in survey results.
```{r}
### ---- standardize-achievement ----
mdf$LevelAchieved <-
  str_replace_all(mdf$LevelAchieved,
                  fixed("Unsatisactory (<60%)"), "Unsatisfactory") # Fix a typo

achievements1 <- c("Unsatisfactory", "Developing", "Basic", "Proficient", "Advanced")
achievements2 <- c("Unacceptable", "Rudimentary", "Fair", "Good", "Excellent")
names(achievements2) <- achievements1 # Named list as dictionary
pttrn <- paste(c(achievements1, achievements2), collapse = "|")

x <- levels(mdf$LevelAchieved)

mdf <- mdf %>% mutate(
  LevelAchieved.Original = LevelAchieved,
  LevelAchieved = str_extract(mdf$LevelAchieved, pttrn))
mdf$LevelAchieved <- str_replace_all(mdf$LevelAchieved, achievements2)
mdf$LevelAchieved <- ordered(mdf$LevelAchieved, levels = achievements2)

summary(mdf$LevelAchieved)
```


```{r}
## ---- new-variables ----
mdf <- mdf %>% mutate(
  Met.UND = case_when(
    is.na(LevelAchieved) ~ "Missing",
    LevelAchieved == "Excellent" | LevelAchieved == "Good" |
      LevelAchieved == "Fair" ~ "Met",
    LevelAchieved == "Rudimentary" | LevelAchieved == "Unacceptable" ~ "Not",
    TRUE ~ "Other"),
  Met.GRD = case_when(
    is.na(LevelAchieved) ~ "Missing",
    LevelAchieved == "Excellent" | LevelAchieved == "Good" ~ "Met",
    LevelAchieved == "Fair" | LevelAchieved == "Rudimentary" |
      LevelAchieved == "Unacceptable" ~ "Not",
    TRUE ~ "Other"),
  Online = grepl("GW", Section),
  Met.UND.bin = Met.UND == "Met",
  Met.GRD.bin = Met.GRD == "Met"
  )
table(mdf$LevelAchieved, mdf$Met.UND, useNA = "ifany")
```

## Follow Up to the Updates
How does the code in analysis change? Shouldn't be much other than variable names... Done.

## Examine Data
```{r}
# Undergrad focus for now
tbl1 <- mdf %>% filter(str_detect(Name, "Major|Minor", negate = TRUE)) %>%
  group_by(Course, Assessment, Name, PLO) %>%
  summarise(Met = mean(Met.UND.bin), n = n())
tbl1
```

Non-rubric data are collected at `Section` level and as shares of students who achieved goals. Use the class size as a weight to have the proper aggregation. Moreover, keep the `PLO Mixed` column for identifying apparently-identical assessments (e.g. different parts of exams).
```{r}
tbl2 <- non %>%
  group_by(Course, Assessment, PLO) %>%
  summarise(Met = weighted.mean(x = np/n, w = n, na.rm = TRUE),
            n = sum(n, na.rm = TRUE), Name = "NA")
tbl3 <- tbl1 %>% bind_rows(tbl2)
summary(tbl3)
```

Mappings are incorporated into the survey.


```{r}
table(tbl3$PLO)
```

```{r}
tbl3 %>% filter(PLO == "ACC 4")
```

Need to have non-rubric data be consistent and contains PLO column. ...Done.
Retrospectively edited the source data file and updated the codes above.

## Outcomes?
Modify the function:
``` r
cname <- "BUS 499"
aname <- "Annotated Bibliography"
oname <- "Plo2"
plo <- 2
tbl3 %>% filter(Course == cname, `Assessment Name` == aname,
                str_detect(Name, oname)) %>% 
  summarize(mean = mean(Met), n = min(n)) %>% mutate(PLO = plo)
```

I *can* summarize by group.
```{r}
tbl3 %>% group_by(PLO) %>% 
  summarize(mean = mean(Met), n = min(n))

```

Really cool. But there's still a problem. Not all the assessments use all the rubric rows. I need to select rubric rows accordingly. (Those PLO markers are placed in the survey data, where each row is at the assessment level.)

```{r}
table(tbl3$PLO)
tbl3 %>% filter(PLO == "ACC 1", str_detect(Name, "NA"))
tbl3 %>% filter(PLO == "ACC 2", str_detect(Name, "NA"))
tbl3 %>% filter(PLO == "BUS 2", str_detect(Name, "Plo2"))
tbl3 %>% filter(PLO == "BUS 5, BUS 6", str_detect(Name, "5[a|b|c|d]")) %>% 
  ungroup() %>% 
  summarize(Met = mean(Met), n = min(n)) %>% mutate(PLO = "BUS 5")
tbl3 %>% filter(PLO == "BUS 5, BUS 6", str_detect(Name, "6[e|f|g]")) %>% 
  summarize(Met = mean(Met), n = min(n)) %>% mutate(PLO = "BUS 6")
tbl3 %>% filter(PLO == "BUS 5, BUS 6", str_detect(Name, "5[a|b|c|d]"))
```

```{r}
get_outcome <- function(plotag, rrow, program, plo){
  if(is.na(plotag)){return(NA)}
  tbl3 %>% filter(PLO == plotag, str_detect(Name, rrow)) %>% ungroup() %>% 
    summarize(Met = mean(Met), n = min(n)) %>%
    mutate(Program = program, PLO = plo)
}
get_outcome(plotag = "BUS 5, BUS 6", rrow = "5[a|b|c|d]",
            program = "Business Core", plo = 5)


```
~~The rest follows.~~

```{r}
#levels(factor(tbl3$PLO))
list.plotags <- list("Accounting" = c("ACC 1", "ACC 2", NA, "ACC 4"),
          "Business Core" = c(NA, "BUS 2", "BUS 3", "BUS 4, BUS 9",
                              "BUS 5, BUS 6", "BUS 5, BUS 6",
                              "BUS 7, BUS 8", "BUS 7, BUS 8", "BUS 4, BUS 9",
                              "BUS 10"),
          "Economics" = c("ECO 2"),
          "HR" = paste("HR", 1:4),
          "Management" = c(rep("MGT 1, MGT 2, MGT 3", 3), "MGT 4"),
          "MBA" = paste("MBA", 1:8)
          )
list.rrows <- list(
  "Accounting" = rep("NA", 4),
  "Business Core" = c(NA, "Plo2", "Plo3", "Plo4", "5[a|b|c|d]", "6[e|f|g]",
                      "Plo7", "Plo8", "Plo9", ".*"),
  "Economics" = c(".*"),
  "HR" = c("Organizational Types",
           "(Organizational Types)|(Organizational Strategy)",
           "Hr Law", ".*"),
  "Management" = c("Plo1", "Plo5", "Plo7", ".*"),
  "MBA" = rep(".*", 8)
  )
# MIS, MKT
```




```{r}
get_outcomes <- function(program){
  # Wrapper to return a combined results for each program
  lres <- list()
  plotags <- list.plotags[[program]]
  rrows <- list.rrows[[program]]
  for(i in 1:length(plotags)){
    lres[[i]] <- get_outcome(plotags[i], rrows[i], program, i)
  }
  lres
}

merge_outcomes <- function(lres){
  # Wrapper function to merge with the historical assessment results
  lres <- lres[!is.na(lres)] # Missing assessment returns NA
  x <- bind_rows(lres)
  x <- x %>% ungroup() %>%
    transmute(`Academic Year` = rep(2019, nrow(x)),
              `Learning Objective Number` = PLO,
              `Outcome` = Met, `Sample Size` = n )
  
  y <- past %>%
    filter(Program == pname, `Assessment Type` == "Internal",
           str_detect(Source, "2020")) %>% 
    select(`Academic Year`, `Learning Objective Number`,
           Outcome, `Sample Size`)
  out <- bind_rows(x, y)
  out
}

getmerge_outcomes <- function(program){
  lres <- get_outcomes(program)
  merge_outcomes(lres)
}

getmerge_outcomes("Accounting")
```


