---
title: "Note to Inspect Rubric Data 4"
date: 6/30/2020
output:
  html_notebook:
    toc: yes
    toc_float:
      collapsed: yes
    code_folding: hide
  html_document:
    toc: yes
    toc_float:
      collapsed: no
    df_print: paged
    code_folding: hide
---

```{r, echo=FALSE, include=FALSE}
#knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
```

# Objective
Data are mostly cleaned and organized through examining each course. Bring back those procedures into the data munging stage and produce the base statistics for Standard 4.

# Set up
Import data. Codes are externalized for reuse. As a reference: `mdf` or main data frame contains the rubric outcome data merged with the course/assessment information gathered from the survey. Data are mostly cleaned up.
```{r}
source('read.R')
source('munge.R')
```

In addition, import the past assessment data (`past`) and the non-rubric assessments provided from the faculty (`non`).
```{r}
past <- read_excel("data/Assessment Data Main.xlsx")
non <- read_excel("data/Non Rubric Data.xlsx")
non <- non %>% transmute(
  Instructor = Name,
  Semester = `In which semester is this course?`,
  Course = paste(Program, Course, Section),
  `Assessment Name` = `What is the name of the assessment you used? (e.g., International Trade Case Study, Final Exam Question 3, etc.)`,
  `Program`, `PLO Mixed`=PLO,
  n = `What is the total number of students that completed the assessment tool for your second learning objective?`,
  pass_n = `If this is an undergraduate assessment, how many students achieved a rubric level of "basic" or scored 70% or better on the assessment?  If this is an MBA formative assessment, how many students s...`,
  Interpretation = `Analysis/Interpretation of Results for your learning objective: Briefly answer the question, What do your assessment data tell us?`,
  Action = `Action for improvement: Briefly explain how you will use the assessment results to make improvements to your course or curriculum.2`)
```

# PLO Measures for Standard 4
We first need simple statistics for the given set of assessment tools. See the `2. Assessment Plan` folder in SharePoint for the latest mappings.

Here is a full list of the rubric outcomes at the rubric-row level disaggregation. Note that most of them are not used for the reporting, but for internal use (detailed analysis and *closing the loop*, or *Standard 6*). The table is organized by `Course` and `Assessment Name`.

The table is comprehensive and long. Skip to the next section ([Business]) if you do not need a particular piece of information.
```{r}
# Undergrad focus for now
tbl <- mdf %>% filter(str_detect(Name, "Major|Minor", negate = TRUE)) %>%
  group_by(Course, `Assessment Name`, Name) %>%
  summarise(Met = mean(Met.UND.bin), n = n())
#  summarise(across(ends_with(".bin"), mean, na.rm = TRUE), n = n())
knitr::kable(tbl, digits=2,
             col.names = c("Course", "Assessment Name",
                           "Criterion (Rubric Row)",
                           "Achieved (share)", "Sample Size (n)"))
```
```{r}
non %>% arrange(Course)
#knitr::kable(non %>% arrange(Course))
```

## Accounting
```{r}
lres <- list()
```

### PLO1
Prepare consolidated financial statements in accordance with current accounting principles generally accepted in the United States of America, and learn how each statement is used for business decision making.

ACC331

Exam question.  Students will be required to prepare GAAP based financial statements and non-GAAP financial statements and assess the impacts of GAAP compliance.
```{r}
x <- non %>% filter(str_detect(Course, "ACC 331"),
                    str_detect(`PLO Mixed`, "LO 1")) %>% 
  mutate(PLO = str_extract(`PLO Mixed`, "\\d"), Met = pass_n/n)
knitr::kable(x %>% select(PLO, `Assessment Name`, "Met", n), dig=2)
lres[["PLO1"]] <- x
```


### PLO2
Compare the impact of alternative costing methods.

ACC331

Exam question.  Students will calculate the cost of produced goods using alternative costing systems and assess the implications of costing system applied.
```{r}
x <- non %>% filter(str_detect(Course, "ACC 331"),
                    str_detect(`PLO Mixed`, "LO 2")) %>% 
  mutate(PLO = str_extract(`PLO Mixed`, "\\d"), Met = pass_n/n)
knitr::kable(x %>% select(`Assessment Name`, "Met", n), dig=2)
lres[["PLO2"]] <- x
```

### PLO3
Apply Federal tax law and regulations in the determination of tax liability.

ACC318

Students complete a tax return on their final exam from start to finish, and calculate their tax liability using the appropriate forms and formulas.

No ACC318? >> Logan Howard. Ed following up.

### PLO4
Conduct audit tests and document the test and conclusions.

ACC441

Students will conduct audit tests and document and explain them.

GW1 Christopher Lyons. Ed following up.
```{r}
x <- non %>% filter(str_detect(Course, "ACC 441")) %>% 
  mutate(PLO = str_extract(`PLO Mixed`, "\\d"), Met = pass_n/n)
knitr::kable(x %>% select(`Assessment Name`, "Met", n), dig=2)
lres[["PLO4"]] <- x
```

### Trend
Collect them into a table and merge with the history.
```{r}
x <- bind_rows(lres)
x <- x %>% ungroup() %>% 
  transmute(`Academic Year` = rep(2019, nrow(x)),
            `Learning Objective Number` = as.numeric(PLO),
            `Outcome` = Met, `Sample Size` = n )
y <- past %>%
  filter(Program == "Accounting", `Assessment Type` == "Internal",
         str_detect(Source, "2020")) %>% 
  select(`Academic Year`, `Learning Objective Number`, Outcome, `Sample Size`)
out <- bind_rows(x, y)
knitr::kable(out %>% filter(`Academic Year`==2019), dig=2)
```

```{r}
title <- "Accounting, Prevalence of Achievments Over Academic Years, by PLO"
caption <- "Grey number represents sample size.\nFor 2019, minimum sample size is used if prevalence is computed from multiple criteria."
ggplot(out,
       aes(`Academic Year`, Outcome, group = `Learning Objective Number`)) +
  geom_line(na.rm = TRUE) +
  geom_point(aes(color = Outcome > 0.7), na.rm = TRUE) +
  scale_colour_manual(values = setNames(c('blue','red'),c(T, F))) +
  geom_text(aes(`Academic Year`, 0.5, label = round(`Sample Size`, 0)),
            alpha = 0.4, na.rm = TRUE) +
  geom_hline(yintercept = 0.7, color = "red") +
  scale_y_continuous(labels=scales::percent) +
  facet_wrap(vars(`Learning Objective Number`)) +
  theme_minimal() +
  labs(title = title, caption = caption) +
  theme(axis.title = element_blank(),
        text = element_text(family = "serif"),
        panel.grid.minor.x = element_blank(),
        legend.position = "none")
```


## Business
```{r}
lres <- list()
```
Most PLOs are explicitly stated in the rubric rows. With some consultation with Beth, most of the outcomes are identified with PLOs.

### PLO1
Both internal/external use Peregrine test. Retrieve information from the data and/or from Ahmet's analysis.

### PLO2
Annotated bibliography (rubric--milestone in company profile)
```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Annotated Bibliography",
         Course == "BUS 499", str_detect(Name, "Plo2"))
knitr::kable(x, dig = 2)
```

It's unclear how to handle rows. Below, I calculate simple/weighted means of spreads of achievements.
```{r}
x <- x %>% mutate(w = Name %>%
                    str_extract("\\d{1,2}%") %>% str_extract("\\d{1,2}"))
res <- x %>% summarize(mean = mean(Met),
                       wmean = weighted.mean(Met, as.numeric(w)),
                       min_n = min(n), max_n = max(n)) %>%
  mutate(PLO = 2)
knitr::kable(res, dig=2)
lres[["PLO2"]] <- res
```

### PLO3
Company profile, rubric graded project.  Rubric rows  PLO3 a, b, c, d, e

PLO3 are found in Company Profile, but not disaggregated. Some of PLO3 (a,b) are in GoVenture AAR. Here, only Comapny Profile is used.
```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Company Profile (Final Paper)",
         Course == "BUS 499", str_detect(Name, "Plo3"))
res <- x %>% summarize(mean = mean(Met),
                       min_n = min(n), max_n = max(n)) %>%
  mutate(PLO = 3)
knitr::kable(x, dig = 2)
lres[["PLO3"]] <- res
```

### PLO4
BUS 499 Capstone Simulation, AAR Rows PLO4 a, b
```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Goventure Aar",
         Course == "BUS 499", str_detect(Name, "Plo4"))
knitr::kable(x, dig = 2)
```

PLO4 can be found in Company Profile as well. Here, ignore it and only use AAR.
```{r}
x <- x %>% mutate(w = Name %>%
                    str_extract("\\d{1,2}%") %>% str_extract("\\d{1,2}"))
res <- x %>% summarize(mean = mean(Met),
                       wmean = weighted.mean(Met, as.numeric(w)),
                       min_n = min(n), max_n = max(n)) %>%
  mutate(PLO = 4)
knitr::kable(res, dig=2)
lres[["PLO4"]] <- res
```

### PLO5 and 6
- PLO5 BUS 499 Company profile project, Rubric rows PLO2 a, b, c, d 
- PLO6 BUS 499 Company profile Rows PLO2 e, f, g

```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Company Profile (Final Paper)",
         Course == "BUS 499", str_detect(Name, "Plo[5-6]"))
knitr::kable(x, dig = 2)
```

Select the specified rows. ...6f and 6g missing?
```{r}
x <- x %>% filter(str_detect(Name, "(5[a|b|c|d])|(6[e|f|g])"))
x <- x %>% mutate(w = Name %>%
                    str_extract("\\d{1,2}%") %>% str_extract("\\d{1,2}"))
res <- x %>%
  mutate(PLO = str_extract(Name, "Plo[1-9]")) %>% 
  group_by(Course, `Assessment Name`, PLO) %>%
  summarize(mean = mean(Met),
                       wmean = weighted.mean(Met, as.numeric(w)),
                       min_n = min(n), max_n = max(n)) %>% 
  mutate(PLO = c(5, 6))
knitr::kable(res, dig=2)
lres[["PLO6"]] <- res[2, ]
lres[["PLO5"]] <- res[1, ]
```

### PLO7 and 8

- PLO7 Internal: BUS 499 International ethics case. Rubric Rows PLO7 a,b,C  
- PLO8 Internal: BUS 499 International ethics case, Rubric Rows PLO8 a,b,C
```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Ethics Case Paper",
         Course == "BUS 499", str_detect(Name, "Plo[7-8]"))
knitr::kable(x, dig = 2)
```

No PLO7c? THere's no information about weights.
```{r}
x <- x %>% filter(str_detect(Name, "[7|8]d", negate = TRUE))
res <- x %>%
  mutate(PLO = str_extract(Name, "Plo[1-9]")) %>% 
  group_by(Course, `Assessment Name`, PLO) %>%
  summarize(mean = mean(Met), min_n = min(n), max_n = max(n)) %>% 
  mutate(PLO = c(7, 8))
knitr::kable(res, dig=2)
lres[["PLO8"]] <- res[2, ]
lres[["PLO7"]] <- res[1, ]
```

### PLO9 
Simulation Peer Feedback #2, total score (BUS 499 Team simulation) Updated: AAR Rubric Rows PLO9a + PLO9b, 90% achieving "usually" or "always"

```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Goventure Aar",
         Course == "BUS 499", str_detect(Name, "Plo9"))
#mdf %>%  filter(`Assessment Name`=="Goventure Aar")
knitr::kable(x, dig = 2)
```

Achievement levels for those are standard (Good, Rudimentary, etc.)?
```{r}
x <- x %>% mutate(w = Name %>%
                    str_extract("\\d{1,2}%") %>% str_extract("\\d{1,2}"))
res <- x %>%
  mutate(PLO = str_extract(Name, "Plo[1-9]")) %>% 
  group_by(Course, `Assessment Name`, PLO) %>%
  summarize(mean = mean(Met),
                       wmean = weighted.mean(Met, as.numeric(w)),
                       min_n = min(n), max_n = max(n)) %>% 
  mutate(PLO = 9)
knitr::kable(res, dig=2)
lres[["PLO9"]] <- res
```

### PLO10
Internal: Final reflection paper. BUS 499 Reflection and Development Plan Rows 1 and 2

This one doesn't have markers. Pick "Challenges" and "Leadership Skills".
```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Development Plan",
         Course == "BUS 499")
knitr::kable(x, dig = 2)
```

```{r}
x <- x %>% filter(str_detect(Name, "(Challenges)|(Leadership)"))
res <- x %>%
  mutate(PLO = str_extract(Name, "Plo[1-9]")) %>% 
  summarize(mean = mean(Met), min_n = min(n), max_n = max(n)) %>% 
  mutate(PLO = 10)
knitr::kable(res, dig=2)
lres[["PLO10"]] <- res
```

### Trend
Collect them into a table and merge with the history.
```{r}
x <- bind_rows(lres)
x <- x %>% ungroup() %>% 
  transmute(`Academic Year` = rep(2019, nrow(x)),
                     `Learning Objective Number` = PLO,
                     `Outcome` = mean,
                     `Sample Size` = min_n )
y <- past %>%
  filter(Program == "Business Core", `Assessment Type` == "Internal",
         str_detect(Source, "2020")) %>% 
  select(`Academic Year`, `Learning Objective Number`, Outcome, `Sample Size`)
out <- bind_rows(x, y)
knitr::kable(out %>% filter(`Academic Year`==2019), dig=2)
```

```{r}
title <- "Business Core, Prevalence of Achievments Over Academic Years, by PLO"
caption <- "Grey number represents sample size.\nFor 2019, minimum sample size is used if prevalence is computed from multiple criteria."
ggplot(out %>% filter(`Learning Objective Number` != 1),
       aes(`Academic Year`, Outcome, group = `Learning Objective Number`)) +
  geom_line(na.rm = TRUE) +
  geom_point(aes(color = Outcome > 0.7), na.rm = TRUE) +
  scale_colour_manual(values = setNames(c('blue','red'),c(T, F))) +
  geom_text(aes(`Academic Year`, 0.5, label = round(`Sample Size`, 0)),
            alpha = 0.4, na.rm = TRUE) +
  geom_hline(yintercept = 0.7, color = "red") +
  scale_y_continuous(labels=scales::percent) +
  facet_wrap(vars(`Learning Objective Number`)) +
  theme_minimal() +
  labs(title = title, caption = caption) +
  theme(axis.title = element_blank(),
        text = element_text(family = "serif"),
        panel.grid.minor.x = element_blank(),
        legend.position = "none")
```

ToDo: PLO 9 has a different threshold (0.9). Address that.

## Economics
```{r}
lres <- list()
```

### PLO1
ECO 301 missing? Not even in the request.

### PLO2
ECO 302 for spring 2020. Information is provided in the form of non-rubric assessment.
```{r}
x <- non %>% filter(str_detect(Course, "ECO 302"),
                    str_detect(`PLO Mixed`, "LO2")) %>% 
  mutate(PLO = str_extract(`PLO Mixed`, "\\d"), Met = pass_n/n)
knitr::kable(x %>% select(PLO, `Assessment Name`, "Met", n), dig=2)
lres[["PLO2"]] <- x
```

### PLO3-5
Rubric rows are not specified in those PLO (3-5) for ECO 421 and hard to guess from PLOs themselves. Ask Ed and Paul.
```{r}
x <- tbl %>% filter(Course == "ECO 421") %>% ungroup() %>% 
  select(Name, Met, n)
knitr::kable(x, dig=2)
```

## Finance
Both are from FIN 302. Only rubric assessments from Chris?

### PLO1
Identify and differentiate financial concepts, theories, and/or methods that are used in making specific business decisions.

### PLO2
Use qualitative and quantitative methods to examine the worthiness of a common business issue.

## Human Resource Management

```{r}
x <-tbl %>% filter(Course == "HRM 400") %>% ungroup() %>% 
  select(`Assessment Name`, Name, Met, n)
knitr::kable(x, dig=2)
```

### PLO1
Choose effective HR strategies that incorporate human and organizational dynamics while leveraging available HR technologies.

### PLO2
Assess effectiveness of HR programs and compensation and benefits plans across organizational types.

### PLO3
LO3: Evaluate HR policy for alignment with current HR Law and ethical HR practices.

### PLO4
Demonstrate effective leadership in a team setting. 

Also, non-rubric assessments are included.
```{r}
x <- non %>% filter(str_detect(Course, "HRM 400")) %>% 
  mutate(Met = pass_n/n)
x
knitr::kable(x %>% select(`Assessment Name`, "Met", n), dig=2)
```


## Management
```{r}
lres <- list()
```

### PLO1
Summative (collected as a single assessment score from the simulation this cycle. Next cycle, will be a two-row rubric in D2L). Alternative assessment for this cycle: PLO1/CLO1 in final paper rubric
```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Ethics Final Paper",
         Course == "BUS 345", str_detect(Name, "Plo1")) %>% 
  mutate(PLO = 1, mean = Met, min_n = n)
knitr::kable(x, dig = 2)
lres[["PLO1"]] <- x
```

### PLO2
Summative (collected as a single assessment score from the simulation this cycle. Next cycle, will be a two-row rubric in D2L) Alternative assessment for this cycle: PLO5a, b, c, d (all CLO2) in final paper rubric

```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Ethics Final Paper",
         Course == "BUS 345", str_detect(Name, "Plo2")) %>% 
  mutate(PLO = 2, mean = Met, min_n = n)
knitr::kable(x, dig = 2)
lres[["PLO2"]] <- x
```


### PLO3
Summative Rows PLO7a, b, c (all CLO3) in final paper rubric
```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Ethics Final Paper",
         Course == "BUS 345", str_detect(Name, "Plo7"))
res <- x %>% summarize(mean = mean(Met),
                       min_n = min(n), max_n = max(n)) %>%
  mutate(PLO = 3)
knitr::kable(res, dig=2)
lres[["PLO3"]] <- res
```

### PLO4
Summative Use overall rubric total from reflection and development plan

"Ethics Reflection"? Name altered earlier?
```{r}
x <- tbl %>%
  filter(`Assessment Name`=="Ethics Reflection",
         Course == "BUS 345")
knitr::kable(x, dig = 2)
```

### Trend
```{r}
x <- bind_rows(lres)
x <- x %>% ungroup() %>% 
  transmute(`Academic Year` = rep(2019, nrow(x)),
                     `Learning Objective Number` = PLO,
                     `Outcome` = mean,
                     `Sample Size` = min_n )
y <- past %>%
  filter(Program == "Economics", `Assessment Type` == "Internal") %>% 
  select(`Academic Year`, `Learning Objective Number`, Outcome, `Sample Size`)
out <- bind_rows(x, y)
knitr::kable(out %>% filter(`Academic Year`==2019), dig=2)
```

```{r}
title <- "Management, Prevalence of Achievments Over Academic Years, by PLO"
caption <- "Grey number represents sample size.\nFor 2019, minimum sample size is used if prevalence is computed from multiple criteria."
ggplot(out %>% filter(`Learning Objective Number` != 4),
       aes(`Academic Year`, Outcome, group = `Learning Objective Number`)) +
  geom_line(na.rm = TRUE) +
  geom_point(aes(color = Outcome > 0.7), na.rm = TRUE) +
  scale_colour_manual(values = setNames(c('blue','red'),c(T, F))) +
  geom_text(aes(`Academic Year`, 0.5, label = round(`Sample Size`, 0)),
            alpha = 0.4, na.rm = TRUE) +
  geom_hline(yintercept = 0.7, color = "red") +
  scale_y_continuous(labels=scales::percent) +
  facet_wrap(vars(`Learning Objective Number`)) +
  theme_minimal() +
  labs(title = title, caption = caption) +
  theme(axis.title = element_blank(),
        text = element_text(family = "serif"),
        panel.grid.minor.x = element_blank(),
        legend.position = "none")
```


## Marketing
All are from MKT401, where rubrics are used.

"Goal 1 is not part of the current internal assessment cycle"? That includes PLO2?

Also, first sheet contains the new PLOs.

MKT PLO1-3 marked with Eric Freeman.

```{r}
x <- tbl %>% filter(Course == "MKT 401") %>% ungroup() %>% 
  select(`Assessment Name`, Name, Met, n)
knitr::kable(x, dig=2)
```

### PLO2
Effectively communicate marketing decisions and processes

### PLO3
Interpret data to support ethical marketing decisions across constituencies



## MBA
~~First sheet is not updated.~~ Check last sheet.
```{r}
lres <- list()
```

### PLO1
Demonstrate ability to solve problems using the tools of accounting

Score on the final exam in ACC 711
```{r}
x <- non %>% filter(str_detect(Course, "ACC 711")) %>% 
  mutate(PLO = 1, Met = pass_n/n)
res <- x %>% select(PLO, `Assessment Name`, "Met", min_n = n)
knitr::kable(res, dig=2)
lres[["PLO1"]] <- res
```

### PLO2
Demonstrate ability to solve problems using the tools of economics

Score on the final exam in ECO 716
```{r}
x <- non %>% filter(str_detect(Course, "ECO 716")) %>% 
  mutate(PLO = 2, Met = pass_n/n)
res <- x %>% select(PLO, `Assessment Name`, "Met", min_n = n)
knitr::kable(res, dig=2)
lres[["PLO2"]] <- res
```

### PLO3
Demonstrate ability to solve problems using the tools of finance

Score on the final exam in FIN 711
```{r}
x <- non %>% filter(str_detect(Course, "FIN 711")) %>% 
  mutate(PLO = 3, Met = pass_n/n)
res <- x %>% summarise(Met = mean(Met), min_n = min(n), max_n = max(n)) %>% 
  mutate(PLO = 3)
knitr::kable(res, dig=2)
lres[["PLO3"]] <- res
```

### PLO4
Demonstrate ability to solve problems using the tools of human resource management

Score on the final exam in HRM 711
```{r}
x <- non %>% filter(str_detect(Course, "HRM 711")) %>% 
  mutate(PLO = 4, Met = pass_n/n)
res <- x %>% select(PLO, `Assessment Name`, "Met", min_n = n)
knitr::kable(res, dig=2)
lres[["PLO4"]] <- res
```

### PLO5
Demonstrate ability to solve problems using the tools of international business

Score on the final exam in MKT 741

Not found in requests. MBA LO5 is missing in requests.

### PLO6
Demonstrate ability to solve problems using the tools of marketing

Score on the final exam in MKT 711
```{r}
x <- non %>% filter(str_detect(Course, "MKT 711")) %>% 
  mutate(PLO = 6, Met = pass_n/n)
res <- x %>% summarise(Met = mean(Met), min_n = min(n), max_n = max(n)) %>% 
  mutate(PLO = 6)
knitr::kable(res, dig=2)
lres[["PLO6"]] <- res
```

### PLO7
Demonstrate ability to solve problems using the tools of strategic management

Score on the final exam in MGT 799

Not found in requests. BUS 799 marked as "MBA LO7". Taught by Paul Redden.

### PLO8
Employ mathematical and statistical techniques in business decision-making

Score on the final exam in BUS 771

```{r}
x <- non %>% filter(str_detect(Course, "BUS 771")) %>% 
  mutate(PLO = str_extract(`PLO Mixed`, "\\d"), Met = pass_n/n)
res <- x %>% summarise(Met = mean(Met), min_n = min(n), max_n = max(n)) %>% 
  mutate(PLO = 8)
knitr::kable(res, dig=2)
lres[["PLO8"]] <- res
```

### Trend
```{r}
x <- bind_rows(lres)
x <- x %>% ungroup() %>% 
  transmute(`Academic Year` = rep(2019, nrow(x)),
                     `Learning Objective Number` = PLO,
                     `Outcome` = Met,
                     `Sample Size` = min_n )
y <- past %>%
  filter(Program == "Business Core", `Assessment Type` == "Internal",
         str_detect(Source, "2020")) %>% 
  select(`Academic Year`, `Learning Objective Number`, Outcome, `Sample Size`)
out <- bind_rows(x, y)
knitr::kable(out %>% filter(`Academic Year`==2019), dig=2)
```

```{r}
title <- "MBA, Prevalence of Achievments Over Academic Years, by PLO"
caption <- "Grey number represents sample size.\nFor 2019, minimum sample size is used if prevalence is computed from multiple criteria."
ggplot(out %>% filter(`Learning Objective Number` != 9, `Learning Objective Number` != 10),
       aes(`Academic Year`, Outcome, group = `Learning Objective Number`)) +
  geom_line(na.rm = TRUE) +
  geom_point(aes(color = Outcome > 0.7), na.rm = TRUE) +
  scale_colour_manual(values = setNames(c('blue','red'),c(T, F))) +
  geom_text(aes(`Academic Year`, 0.5, label = round(`Sample Size`, 0)),
            alpha = 0.4, na.rm = TRUE) +
  geom_hline(yintercept = 0.7, color = "red") +
  scale_y_continuous(labels=scales::percent) +
  facet_wrap(vars(`Learning Objective Number`)) +
  theme_minimal() +
  labs(title = title, caption = caption) +
  theme(axis.title = element_blank(),
        text = element_text(family = "serif"),
        panel.grid.minor.x = element_blank(),
        legend.position = "none")
```

## MIS
MIS 401 (MGT 373)

Not requested? Use just exams?

### PLO1
Evaluate how database management software helps business professionals and supports the operations and management of a business.

### PLO2
Evaluate the role of planning and business models in the development of business/IT strategies, architectures, and applications.

